\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Yug Gajjar} \\ \vspace{2pt}
    \small \href{mailto:yug.gjr@gmail.com}{\underline{yug.gjr@gmail.com}} $|$ 
    \href{https://linkedin.com/in/yug-gajjar-34222b18b/}{\underline{LinkedIn}} $|$
    \href{https://github.com/Yug34}{\underline{Github}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Gujarat Technological University}{}
      {Bachelor of Technology in Electronics and Communication}{Aug. 2018 -- Expected Sept. 2022}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Research Assistant}{Aug. 2020 -- Present}
      {\small{Supervised by: \href{https://scholar.google.com/citations?user=1lVSmQwAAAAJ&hl=en}{\underline{Dr. Wouter Deconinck}}}}{University of Manitoba}
      \resumeItemListStart
        \resumeItem{Implemented a system to locate data resources for Jefferson Lab's  \href{https://moller.jlab.org/moller_root/}{\underline{MOLLER Experiment}} at  \href{https://github.com/jeffersonlab/remoll/}{\underline{remoll}} irrespective of the directory it is started from.}
        \resumeItem{Helped with containerizing \href{https://hub.docker.com/r/jeffersonlab/remoll/}{\underline{remoll for Docker}} and \href{https://sylabs.io/}{\underline{Singularity}}.}
        \resumeItem{Currently trying to have the Singularity image work with super-computing on  \href{https://opensciencegrid.org/}{\underline{OpenScienceGrid}} for high throughput simulations with HTCondor.}
    \resumeItemListEnd
      
    \resumeSubheading
      {Front-End Developer}{Nov. 2020 -- Present}
      {IEEE, VGEC}{Remote}
      \resumeItemListStart
        \resumeItem{Revamping the website of IEEE, VGEC.}
        \resumeItem{Working on making the website mobile responsive.}
    \resumeItemListEnd
      
    \resumeSubheading
      {Full-Stack Developer}{Oct. 2020 -- Feb. 2021}
      {Freelancing}{}
      \resumeItemListStart
        \resumeItem{Worked with a client to create a MERN stack web app.}
        \resumeItem{Implemented a web-player to play videos in the browser.}
        \resumeItem{Used \emph{three.js} for animations.}
        \resumeItem{Implemented REST API endpoints.}
    \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
    % \resumeSubSubheading
    % {Software Engineer I}{Oct 2014 - Sep 2016}
    % \resumeItemListStart
    %     \resumeItem{Apache Beam}
    %      {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
    % \resumeItemListEnd
    % \resumeSubHeadingListEnd
% -------------------------------------------
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Seamless} $|$ \emph{Postgres, Express, React, Node.js, Docker, Netlify}}{Dec 2020 -- Present}
          \resumeItemListStart
            \resumeItem{Developing a full-stack music player as the final project for      \href{http://theodinproject.com/}{\underline{The Odin Project}} that allows a user to play their Youtube and  Spotify playlists from a single web app.}
            \resumeItem{Implemented OAuth to fetch user's playlist data from YouTube and Spotify.}
            \resumeItem{Implemented Cross-Origin requests for YouTube audio streaming.}
            \resumeItem{Will be publicly hosted on Netlify and open-sourced on Github after refactor.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{AllBOT} $|$ \emph{Discord.js, Node.js, SQLite, Sequelize, Heroku, Docker}}{Sept 2020 -- Present}
          {\small{\item{\href{https://github.com/Yug34/allBOT}{\underline{Source code}}}}} $||$  {\small{\href{https://discord.com/oauth2/authorize?client_id=765198269068083200&permissions=8&scope=bot}{\underline{Invite Bot}}}} $||$  {\small{\href{https://discord.gg/rYSdQsFB}{\underline{Join Bot Server}}}}  
          \resumeItemListStart
            \resumeItem{Developed multi-purpose Discord bot.}
            \resumeItem{Implemented functionality for the bot to stream music from YouTube.}
            \resumeItem{Implemented a guild-centered currency system for the bot.}
            \resumeItem{Implemented games interfacing with the currency system.}
            \resumeItem{Implemented several commands that interact with API end-points and admin commands.}
            \resumeItem{Hosted on Heroku.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{PortfolioGen} $|$ \emph{React.js, Redux, jQuery, three.js, tilt.js, vanta.js}}{Jan 2021 -- Present}
          \resumeItemListStart
            \resumeItem{Developing a web application that takes user data, processes it, and dynamically generates another web application that is a portfolio.}
            \resumeItem{Implemented logic to process the user data into JSON.}
            \resumeItem{Implemented a converter to generate components from the data in the JSON object.}
            \resumeItem{Will be publicly hosted and open-sourced on Github after refining.}
      \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{CRUD Blog API} $|$ \emph{Django, js, Python, AWS S3 \& IAM, SQLite(test), Postgres(prod), Heroku}}{Mar 2020}
          {\small{\item{\href{https://github.com/Yug34/stupid-blog}{\underline{Source code}}}}} $||$ {\small{\href{https://mystupidblog.herokuapp.com/}{\underline{View Live}}}}
          \resumeItemListStart
          \resumeItem{Created a CRUD blogging web application with Django framework in Python.}
          \resumeItem{Used JavaScript to generate background animation.}
          \resumeItem{Implemented fetching of data and images that are stored in AWS S3 buckets.}
          \resumeItem{Implemented user authentication, allowing users to create profiles and edit profiles, post and edit their posts.}
          \resumeItem{Hosted on Heroku.}
      \resumeItemListEnd
    \resumeSubHeadingListEnd
%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: \emph{Proficient in}: JavaScript, Python, C++, HTML5, CSS3 $|$ $|$ \emph{Worked with}: Java, C, Bash} 
     \textbf{\newline Frameworks/Libraries}{: React, Redux.js, Router, Node.js, Express, Django, React-Bootstrap, Bootstrap, React-Router, Jest, SASS} \\
     \textbf{Databases}{: MongoDB, MySQL, Postgres, SQLite} \\
     \textbf{Developer Tools}{: Linux, Git, Docker, Spack, CMake, Singularity, Webpack, Babel, TravisCI, WebStorm, ESLint, Github Actions} \\
    }}
 \end{itemize}
 
 
%------------ Languages -----------------%
\section{Languages}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{English}{: Fluent} \newline
     \textbf{Hindi}{: Native} \newline
     \textbf{Gujarati}{: Native}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
